---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gibbonID

<!-- badges: start -->
<!-- badges: end -->

The goal of gibbonID is make clustering and visualization of acoustic data in R easy! This package is currently under development with a planned full release later this year (2022).

## Installation

You can install the development version from [GitHub](https://github.com/DenaJGibbon) with:
```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("DenaJGibbon/gibbonID")
```

## Example

This is a basic example which shows you how to create a biplot using gibbonID. Our dataset consists of different female Northern Gray gibbons:
```{r echo=FALSE, message=FALSE}
devtools::load_all()
```


```{r warning=FALSE, message=FALSE}
library(gibbonID)
library(ggpubr)

ExampleBiplot <- gibbonID::UMAPBiplotAddSpectrograms(input.dir.Focal="/Users/denaclink/Desktop/RStudio Projects/gibbonID/data/FocalTest",
                          output.dir.Focal = "/Users/denaclink/Desktop/RStudio Projects/gibbonID/data/FocalTest/Thumbnails/",
                          min.freq = 400, max.freq = 1800,main='Female Gibbon Calls')

 
```

```{r dpi=300}
ExampleBiplot 
```
